Beam-Helicity and Beam-Charge Asymmetries \\ in the Bethe-Heitler and DVCS processes on \\ an Unpolarised Proton Target \underline{Paper Tag: PDVCS0607 (v1.2)} \underline{Drafting Committee: DC90 (\today)}

### 2011-08-31 results_dual.tex
Cosmetic changes, ready for second circulation

The results of the beam-helicity and beam-charge asymmetry amplitudes extracted from the complete 1996-2007 hydrogen sample are shown in Figs.~\ref{bsa_xbjrange} and \ref{bca_xbjrange}. The number of analysable events available from the 2006-2007 data set (70352) is approximately three times greater than the number of events recorded in the 1996-2005 sample (24817). The  asymmetry amplitudes extracted from the complete 1996-2007 data set thus resemble the 2006-2007 result. This resemblance is not so evident for the beam-helicity asymmetry amplitudes because the beam polarisation was lower in 2006 and 2007 than in 1996-2005, giving the 2006\red{-}2007 data a lower weighting in the combined fit.

The first and second harmonics of $\mathcal{A}_{\textrm{LU,I}}$, which are
sensitive to the interference term in the scattering amplitude, are shown in the first and third rows of Fig.~\ref{bsa_xbjrange}. The leading-twist amplitude $A_{\textrm{LU,I}}^{\sin\phi}$ has the largest magnitude of any of the amplitudes when extracted in a single bin from the entire data set. This amplitude shows no strong dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$, implying a strong dependence at smaller values of $-t$ as the amplitude must approach zero as $-t$ approaches zero due to the dependence of the amplitude on the factor $k$ from Eq.~\ref{eq:s1}. The $A_{\textrm{LU,I}}^{\sin\phi}$ amplitude is sensitive to the imaginary part of the CFF $\mathcal{H}$ and thereby can constrain GPD $\textit{H}$. The $A_{\textrm{LU,DVCS}}^{\sin\phi}$ asymmetry is shown in the second row of Fig.~\ref{bsa_xbjrange}. Both the $A_{\textrm{LU,DVCS}}^{\sin\phi}$ asymmetry amplitude and the $A_{\textrm{LU,I}}^{\sin(2\phi)}$ asymmetry amplitude are compatible with zero, and neither asymmetry amplitude shows any dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$. The systematic error bands associated with the asymmetry amplitudes extracted from the combined data set were determined using Monte Carlo simulations as explained in section~4. The missing-mass uncertainty for the combined data set was calculated using the procedure described in that section and the results were added in quadrature.

>>>>

The results of the beam-helicity and beam-charge asymmetry amplitudes extracted from the complete 1996-2007 hydrogen sample are shown in Figs.~\ref{bsa_xbjrange} and \ref{bca_xbjrange}. The number of analysable events available from the 2006-2007 data set (70352) is approximately three times greater than the number of events recorded in the 1996-2005 sample (24817). The  asymmetry amplitudes extracted from the complete 1996-2007 data set thus resemble the 2006-2007 result. This resemblance is not so evident for the beam-helicity asymmetry amplitudes because the beam polarisation was lower in 2006 and 2007 than in 1996-2005, giving the 2006\red{-}2007 data a lower weighting in the combined fit. \red{The systematic error bands associated with the asymmetry amplitudes extracted from the combined data set were determined using Monte Carlo simulations as explained in section~4. The missing-mass uncertainty for the combined data set was calculated using the procedure described in that section and the results were added in quadrature.}

The first and second harmonics of $\mathcal{A}_{\textrm{LU,I}}$, which are
sensitive to the interference term in the scattering amplitude, are shown in the first and third rows of Fig.~\ref{bsa_xbjrange}. The leading-twist amplitude $A_{\textrm{LU,I}}^{\sin\phi}$ has the largest magnitude of any of the amplitudes when extracted in a single bin from the entire data set. This amplitude shows no strong dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$, implying a strong dependence at smaller values of $-t$ as the amplitude must approach zero as $-t$ approaches zero due to the dependence of the amplitude on the factor $k$ from Eq.~\ref{eq:s1}. The $A_{\textrm{LU,I}}^{\sin\phi}$ amplitude is sensitive to the imaginary part of the CFF $\mathcal{H}$ and thereby can constrain GPD $\textit{H}$. The $A_{\textrm{LU,DVCS}}^{\sin\phi}$ asymmetry is shown in the second row of Fig.~\ref{bsa_xbjrange}. Both the $A_{\textrm{LU,DVCS}}^{\sin\phi}$ asymmetry amplitude and the $A_{\textrm{LU,I}}^{\sin(2\phi)}$ asymmetry amplitude are compatible with zero, and neither asymmetry amplitude shows any dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$.

### 2011-08-31 summary.tex
Fixed bugs in update
Cosmetic changes, ready for second circulation

Beam-helicity and beam-charge asymmetries in the azimuthal distribution of real photons from leptoproduction on an unpolarised hydrogen target have been presented. These asymmetries were extracted from a new unpolarised hydrogen data set taken during the 2006 and 2007 operating periods of H{\sc ermes}. Analogous asymmetry amplitudes were extracted previously from hydrogen data obtained during the 1996-2005 experimental period as described in Ref.~\cite{Air09}. A comparison of the amplitudes extracted from these independent data sets has shown that they are compatible and the asymmetry amplitudes can therefore be extracted from the complete 1996-2007 event sample. \red{The asymmetry amplitudes extracted from the combined data set are the statistically most precise DVCS measurements presented by H{\sc ermes}. There is} a strong signal in the first harmonic of the interference contribution to the beam-helicity asymmetry. There are non-zero amplitudes in the zeroth and first harmonics of the beam-charge asymmetry. Each of the higher order asymmetry amplitudes is consistent with zero. The combined results are compared to calculations from ongoing work to fit GPD models to experimental data. All data amplitudes are also presented as projections in $-t$ in bins of $x_{\textrm{B}}$. No additional features are observed in any particular $\red{x_{\textrm{B}}}$-bin.

\acknowledgments
We gratefully acknowledge the \desy\ management for its support and the staff
at \desy\ and the collaborating institutions for their significant effort.
This work was supported by 
the Ministry of Economy and the Ministry of Education and Science of Armenia;
the FWO-Flanders and IWT, Belgium;
the Natural Sciences and Engineering Research Council of Canada;
the National Natural Science Foundation of China;
the Alexander von Humboldt Stiftung,
the German Bundesministerium f\"ur Bildung und Forschung (BMBF), and
the Deutsche Forschungsgemeinschaft (DFG);
the Italian Istituto Nazionale di Fisica Nucleare (INFN);
the MEXT, JSPS, and G-COE of Japan;
the Dutch Foundation for Fundamenteel Onderzoek der Materie (FOM);
the Russian Academy of Science and the Russian Federal Agency for 
Science and Innovations;
the U.K.~Engineering and Physical Sciences Research Council, 
the Science and Technology Facilities Council,
and the Scottish Universities Physics Alliance;
the U.S.~Department of Energy (DOE) and the National Science Foundation (NSF);
and the European Community Research Infrastructure Integrating Activity
under the FP7 "Study of strongly interacting matter (HadronPhysics2, Grant
Agreement number 227431)".

>>>>

Beam-helicity and beam-charge asymmetries in the azimuthal distribution of real photons from leptoproduction on an unpolarised hydrogen target have been presented. These asymmetries were extracted from a new unpolarised hydrogen data set taken during the 2006 and 2007 operating periods of H{\sc ermes}. Analogous asymmetry amplitudes were extracted previously from hydrogen data obtained during the 1996-2005 experimental period as described in Ref.~\cite{Air09}. A comparison of the amplitudes extracted from these independent data sets has shown that they are compatible and the asymmetry amplitudes can therefore be extracted from the complete 1996-2007 event sample. \red{The asymmetry amplitudes extracted from the combined data set are the statistically most precise DVCS measurements presented by H{\sc ermes}. There is} a strong signal in the first harmonic of the interference contribution to the beam-helicity asymmetry. There are non-zero amplitudes in the zeroth and first harmonics of the beam-charge asymmetry. Each of the higher order asymmetry amplitudes is consistent with zero. The combined results are compared to calculations from ongoing work to fit GPD models to experimental data. All data amplitudes are also presented as projections in $-t$ in bins of $x_{\textrm{B}}$. No additional features are observed in any particular $x_{\textrm{B}}$-bin.

\acknowledgments
We gratefully acknowledge the \desy\ management for its support and the staff
at \desy\ and the collaborating institutions for their significant effort.
This work was supported by 
the Ministry of Economy and the Ministry of Education and Science of Armenia;
the FWO-Flanders and IWT, Belgium;
the Natural Sciences and Engineering Research Council of Canada;
the National Natural Science Foundation of China;
the Alexander von Humboldt Stiftung,
the German Bundesministerium f\"ur Bildung und Forschung (BMBF), and
the Deutsche Forschungsgemeinschaft (DFG);
the Italian Istituto Nazionale di Fisica Nucleare (INFN);
the MEXT, JSPS, and G-COE of Japan;
the Dutch Foundation for Fundamenteel Onderzoek der Materie (FOM);
the Russian Academy of Science and the Russian Federal Agency for 
Science and Innovations;
the U.K.~Engineering and Physical Sciences Research Council, 
the Science and Technology Facilities Council,
and the Scottish Universities Physics Alliance;
the U.S.~Department of Energy (DOE) and the National Science Foundation (NSF);
the Basque Foundation for Science (IKERBASQUE);
and the European Community Research Infrastructure Integrating Activity
under the FP7 "Study of strongly interacting matter (HadronPhysics2, Grant
Agreement number 227431)".
